\section{Introduction}
\label{sec:introduction}

The snatch is a technically demanding Olympic weightlifting movement in which an athlete lifts a barbell from the platform to overhead in one continuous motion.
Coaching, talent identification, and biomechanical research all depend on decomposing the lift into phases such as the first pull, transition, second pull, turnover, catch, and recovery.
Phase-aware analysis supports feedback on bar--body coordination, timing errors, and injury-relevant movement patterns \todosource{weightlifting coaching and biomechanics survey}.

\subsection{Motivation and practical importance}

Competition and training environments generate large volumes of monocular video, but expert phase labeling is time-consuming, subjective, and difficult to standardize across analysts.
Automated temporal phase segmentation could reduce annotation burden, enable retrospective analysis of large archives, and support decision aids in coaching workflows.
However, deployment in applied settings requires not only predictive accuracy but also transparent data handling, reproducible splits, and evaluation protocols that reflect how predictions will be used (window classification, frame-wise labels, or contiguous segments).

\subsection{Marker-based versus markerless analysis}

Laboratory \acs{MOCAP} with optical markers or wearable \acs{IMU}s remains the gold standard for high-precision kinematics \todosource{marker-based biomechanics methods}.
These systems are costly, require controlled capture conditions, and are rarely available during routine training or competition filming.
Markerless pose estimation from monocular video has matured rapidly within \acs{CV} \todosource{markerless pose estimation review}, offering a scalable intermediate representation: a skeleton time series that can feed downstream temporal models.
The trade-off is increased pose noise, occlusions, and domain shift relative to instrumented capture, which must be accounted for when interpreting segmentation performance.

\subsection{Temporal phase segmentation as a learning problem}

Snatch phase identification is an instance of \acf{TAS}: given a temporal sequence of observations, assign a phase label to each time index (or predict contiguous phase segments).
Unlike isolated gesture recognition from trimmed clips, weightlifting videos contain continuous motion with brief but biomechanically critical transitions.
Class imbalance, athlete-specific styles, and subtle differences between adjacent phases (e.g.\ transition versus second pull) make the task non-trivial even when pose inputs are available.

\subsection{Reproducibility gap}

Recent sports analytics and biomechanics studies increasingly employ \acs{DL} pipelines combining pose estimation and temporal models \todosource{sports analytics with pose estimation}.
Nevertheless, it remains difficult for independent groups to verify reported numbers because raw videos, exact splits, preprocessing code, and trained checkpoints are often unavailable or exported incompletely.
During an independent audit and reproduction effort associated with this project, we confirmed that processed tensors can be rebuilt exactly from released annotations and pose CSV files, while some binary artifacts (frozen tensors and the original checkpoint) were distributed as incomplete copies in one export.
This experience motivates \emph{SnatchPhaseBench} as a reproducibility-first benchmark rather than a one-off model description.

\subsection{Scope of this manuscript}

This paper documents the current verified state of SnatchPhaseBench.
The scientific narrative targets a reproducible benchmark for temporal phase segmentation in Olympic weightlifting using markerless pose estimation.
The frozen \acs{LSTM} classifier from prior thesis work serves as an initial baseline implementation; it is not positioned as the final scientific contribution.
Comparative evaluation of alternative temporal architectures (e.g.\ \acs{GRU}, \acs{TCN}, multi-stage \acs{TCN}, \acs{ST-GCN}, Transformers) is planned within a unified protocol but is intentionally deferred until the original baseline checkpoint has been validated.

\subsection{Contributions}
\label{sec:contributions}

The following items reflect \emph{verified} project status at the time of writing.
Items marked \emph{(provisional)} require additional evidence before they can be stated as finalized contributions in a journal submission.

\begin{itemize}
  \item \textbf{Reproducible dataset artifact (verified).}
        A snatch dataset comprising \numvideos{} annotated attempts from \numathletes{} athletes, with frame- and segment-level labels and MediaPipe Pose Landmarker keypoints (\numlandmarks{} landmarks, \featuredim{} coordinates per frame).
        Rebuilding processed tensors from source files reproduces the published manifest checksums for \texttt{X.npy} and \texttt{y.npy}.

  \item \textbf{Athlete-level evaluation split (verified).}
        A fixed split assigning 49, 10, and 11 athletes to training, validation, and test sets, yielding 14{,}140, 3{,}232, and 3{,}877 sliding windows respectively, with no athlete or video overlap across splits.

  \item \textbf{Documented preprocessing and baseline protocol (verified).}
        A configuration-driven pipeline (window size~\windowsize, stride~1, center-frame labeling) and a frozen \acs{LSTM} training recipe with class weighting and train-only standardization, implemented in the public SnatchPhaseBench repository.

  \item \textbf{Extensible evaluation framework (verified infrastructure; benchmark metrics pending).}
        Software modules for window-, frame-, and segment-level metrics (including edit score and segmental F1 at IoU thresholds) are implemented; segment-level benchmark numbers are \emph{not} yet reported.

  \item \textbf{Multi-model benchmark comparison (provisional).}
        Planned comparison of temporal architectures under a shared protocol.
        \Cref{sec:results,sec:discussion} will be populated only after checkpoint validation and benchmark experiments.

  \item \textbf{Public dataset release (provisional).}
        Legal review and pseudonymization of athlete identifiers are pending before public distribution.
\end{itemize}

\subsection{Paper organization}

\Cref{sec:related} reviews related work in biomechanics, markerless pose estimation, and temporal segmentation.
\Cref{sec:dataset} describes the SnatchPhaseBench dataset and splits.
\Cref{sec:methods} presents the verified preprocessing pipeline and \acs{LSTM} baseline; subsections for future benchmark models are reserved.
\Cref{sec:protocol} specifies reproducibility practices and evaluation strategy.
\Cref{sec:results} defines tables and figures but deliberately omits unverified numbers.
\Cref{sec:discussion,sec:limitations,sec:conclusion} provide structured placeholders for interpretation once benchmark evidence is available.
