\section{Related Work}
\label{sec:related}

This section situates SnatchPhaseBench within biomechanical analysis, markerless pose estimation, skeleton-based action understanding, temporal segmentation, and weightlifting-specific studies.
Citations are intentionally omitted until verified bibliographic entries are added to \texttt{bibliography.bib}; each subsection ends with explicit \textsc{TODO} markers for literature to be inserted.

\subsection{Marker-based biomechanical analysis}
\label{sec:related:mocap}

Optical \acs{MOCAP} and force-plate instrumentation enable precise joint-angle and barbell kinematics in controlled laboratory settings \todosource{optical motion capture in sport}.
Such systems have supported detailed snatch and clean-and-jerk analyses, including phase definitions tied to barbell and joint trajectories \todosource{weightlifting biomechanics with MOCAP}.
Limitations for large-scale deployment include calibration overhead, marker placement requirements, and poor transfer to competition footage.

\textbf{Relevance to SnatchPhaseBench.}
Our benchmark adopts phase labels compatible with coaching-oriented snatch decomposition but uses monocular pose inputs rather than marker trajectories.
Future work may compare model predictions against instrumented references where available; no such paired capture is included in the current dataset.

\textsc{TODO:} Add 4--6 verified citations on marker-based Olympic weightlifting biomechanics and phase definitions.

\subsection{Markerless pose estimation}
\label{sec:related:pose}

Top-down and bottom-up human pose estimators produce 2D or 3D skeletons from RGB video \todosource{2D/3D pose estimation surveys}.
MediaPipe Pose Landmarker provides lightweight, real-time 33-landmark estimates including relative depth coordinates \todosource{MediaPipe pose documentation or peer-reviewed validation}.
In sports, pose pipelines have been applied to exercise recognition, technique assessment, and injury screening \todosource{pose estimation in sports}.

\textbf{Relevance to SnatchPhaseBench.}
We use fixed, precomputed MediaPipe keypoints as input features rather than end-to-end video models.
This isolates temporal segmentation from pose-estimator training but introduces dependence on estimator errors and domain shift.

\textsc{TODO:} Add citations comparing OpenPose, HRNet, BlazePose/MediaPipe, and sports-specific pose validation studies.

\subsection{Skeleton-based action recognition}
\label{sec:related:action}

Graph and sequence models operating on skeleton streams perform competitively on action recognition benchmarks such as NTU RGB+D and Kinetics-Skeleton \todosource{skeleton-based action recognition}.
These methods typically classify entire clips or short segments rather than densely label long continuous performances.

\textbf{Relevance to SnatchPhaseBench.}
Weightlifting phases unfold within a single continuous attempt; the task aligns more closely with dense temporal labeling than with trimmed clip classification.
Benchmark models such as \acs{ST-GCN} and Transformer encoders over skeleton tokens are candidates for Phase~3 experiments (\Cref{sec:methods:benchmark}).

\textsc{TODO:} Add skeleton action recognition references and clarify distinction from dense segmentation.

\subsection{Temporal action segmentation}
\label{sec:related:tas}

\acf{TAS} methods predict frame-wise labels or contiguous segments in untrimmed videos \todosource{temporal action segmentation surveys}.
Architectures include temporal convolutional networks, multi-stage refinement (\acs{TCN} variants), and attention-based models \todosource{MS-TCN, ASFormer, etc.}.
Evaluation commonly reports frame-wise accuracy, segmental F1 at IoU thresholds, and edit score \todosource{TAS evaluation metrics}.

\textbf{Relevance to SnatchPhaseBench.}
The current verified baseline uses window-level classification with stride~1, which differs from standard \acs{TAS} evaluation on segment metrics.
The project's evaluation framework implements segment-level metrics for future benchmark reporting (\Cref{sec:protocol:metrics}).

\textsc{TODO:} Add canonical \acs{TAS} citations; map planned benchmark models (GRU, TCN, MS-TCN, Transformer) to this literature.

\subsection{Sports analytics and coaching applications}
\label{sec:related:sports}

Automated analysis of resistance-training exercises includes rep counting, form scoring, and phase detection for exercises such as squats and weightlifting derivatives \todosource{exercise recognition and coaching AI}.
Deployment constraints include interpretability for coaches, robustness to camera viewpoints, and athlete-to-athlete generalization.

\textbf{Relevance to SnatchPhaseBench.}
Our athlete-level split explicitly tests generalization to unseen lifters.
Practical implications are discussed only after benchmark evidence is available (\Cref{sec:discussion}).

\textsc{TODO:} Add sports analytics and coaching-system references.

\subsection{Olympic weightlifting analysis with computer vision}
\label{sec:related:wl}

Computer vision studies on weightlifting have explored barbell tracking, body pose, and lift classification \todosource{weightlifting computer vision}.
Public datasets with frame-wise snatch phase labels and fixed evaluation splits remain limited, hindering comparison across methods.

\textbf{Gap addressed by SnatchPhaseBench.}
We provide a documented dataset, exact preprocessing, athlete-level splits, and a reproducibility-oriented codebase.
Comparative superiority of any single model is \emph{not} claimed at this stage.

\textsc{TODO:} Add weightlifting-specific vision papers; include comparison table mapping prior work vs.\ SnatchPhaseBench protocol (columns: public data, phases, split type, metrics).

\subsection{Positioning of future benchmark comparisons}
\label{sec:related:benchmark_plan}

Future experimental sections will compare temporal models under identical pose inputs, splits, and random seeds.
\Cref{tab:benchmark_comparison} (currently a placeholder shell) will report window-level and segment-level metrics side by side.
Related work will be updated to contextualize benchmark rankings only after those numbers are verified.

\textsc{TODO:} After Phase~3 experiments, add paragraph interpreting results relative to prior weightlifting and \acs{TAS} studies.
