\section{Discussion}
\label{sec:discussion}

This section provides a structured outline for interpreting SnatchPhaseBench results once benchmark experiments are complete.
No performance claims are made at the current manuscript stage.

\subsection{Interpretation of baseline performance}
\label{sec:discussion:interpretation}

\textsc{TODO:} After checkpoint validation, interpret window-level baseline metrics relative to class imbalance (\Cref{tab:class_distribution}) and known difficulty of transition phases.
\textsc{TODO:} Compare checkpoint vs.\ retrain reproduction gap and attribute to hardware, stochasticity, or implementation differences only with evidence.

\subsection{Overlap and metric choice}
\label{sec:discussion:overlap}

\textsc{TODO:} Discuss how stride-1 window evaluation affects apparent accuracy vs.\ segment-level scores.
\textsc{TODO:} Reference temporal autocorrelation analysis in the repository; quantify correlation among adjacent test windows.

\subsection{Benchmark comparison across temporal architectures}
\label{sec:discussion:benchmark}

\textsc{TODO:} Summarize ranking from \Cref{tab:benchmark_comparison} without overclaiming statistical significance until \Cref{sec:protocol:stats} is executed.
\textsc{TODO:} Relate differences to receptive field, parameter count, and suitability for short vs.\ long phase durations.

\subsection{Comparison with prior work}
\label{sec:discussion:prior}

\textsc{TODO:} Position SnatchPhaseBench metrics relative to prior weightlifting studies cited in \Cref{sec:related:wl} once bibliography is complete.
\textsc{TODO:} Clarify that direct numeric comparison may be impossible if splits and labels differ.

\subsection{Practical implications for coaching and sports science}
\label{sec:discussion:practice}

\textsc{TODO:} Discuss whether segment-level accuracy is sufficient for automated feedback tools.
\textsc{TODO:} Address deployment constraints: monocular club footage, real-time latency, interpretability for coaches.

\subsection{Threats to validity}
\label{sec:discussion:validity}

\paragraph{Internal validity.}
\textsc{TODO:} Overlapping windows, single annotation pass, pose estimator bias.

\paragraph{External validity.}
\textsc{TODO:} Athlete cohort diversity, camera conditions, generalization to other weightlifting movements (clean and jerk).

\paragraph{Construct validity.}
\textsc{TODO:} Alignment between operational phase labels and biomechanical theory once definitions are finalized.

\subsection{Future work}
\label{sec:discussion:future}

\textsc{TODO:} Public release, multi-annotator study, paired MOCAP subset, barbell tracking fusion, cross-movement transfer, real-time demo.
