\section{Limitations}
\label{sec:limitations}

We report limitations supported by the Phase~1 audit and Phase~2 reproduction effort.
Speculative limitations without evidence are avoided.

\begin{itemize}
  \item \textbf{Single cohort and setting.}
        All verified attempts come from one curated collection (\numvideos{} videos, \numathletes{} athletes) with unknown camera diversity until metadata are confirmed (\Cref{sec:dataset:videos}).

  \item \textbf{Monocular pose inputs.}
        The benchmark relies on 2D/2.5D MediaPipe landmarks rather than multi-view or instrumented kinematics, limiting direct comparison to laboratory \acs{MOCAP} studies.

  \item \textbf{Dependence on pose estimation quality.}
        Errors in occluded or fast phases (turnover, catch) propagate to temporal models; pose error has not been quantified on this dataset.

  \item \textbf{Manual annotation without inter-rater study.}
        Phase labels reflect the source thesis annotation protocol; inter-annotator agreement and adjudication rules are undocumented.

  \item \textbf{Incomplete public artifact in one export.}
        Binary files (\texttt{best\_model.pt}, frozen \texttt{X.npy}/\texttt{y.npy}, MediaPipe task file) were distributed as Git LFS pointers in an exported snapshot, blocking exact checkpoint evaluation until binaries are obtained.

  \item \textbf{Checkpoint validation pending.}
        Thesis metrics preserved in \texttt{classification\_report.json} have not been re-validated on the original trained weights in the canonical reproduction environment.

  \item \textbf{Window-level baseline protocol.}
        Stride-1 sliding windows create strongly correlated samples from the same video; window-level accuracy may overstate independent generalization performance relative to segment-level metrics.

  \item \textbf{Class imbalance.}
        Transition and second pull contain far fewer windows than setup and recovery (\Cref{tab:class_distribution}), affecting macro-averaged metrics.

  \item \textbf{Legal and privacy constraints.}
        Public release requires pseudonymization and clearance of video rights; athlete identifiers in folder names remain sensitive.

  \item \textbf{Single fixed split.}
        One athlete-level partition (49/10/11) may not capture variance in split assignment; cross-validation is planned but not yet executed.

  \item \textbf{Benchmark scope not yet evaluated.}
        Alternative temporal architectures and segment-level benchmark numbers are planned infrastructure only; no comparative scientific conclusions can be drawn yet.
\end{itemize}
