\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{microtype}
\usepackage[margin=2.5cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,capitalise,noabbrev]{cleveref}

% TODO: Select target venue template (e.g.\ Elsevier \texttt{elsarticle},
% IEEE \texttt{IEEEtran}) before journal submission.

\input{macros}

\title{SnatchPhaseBench: A Reproducible Benchmark for Temporal Phase Segmentation in Olympic Weightlifting from Markerless Pose Estimation}
\author{%
  % TODO: Author names and affiliations after collaboration agreement.
  Anonymous Authors
}
\date{} % omit draft date in submission version

\begin{document}
\maketitle

\begin{abstract}
\noindent
Automatic analysis of Olympic weightlifting technique requires reliable identification of biomechanical phases within each lift attempt.
Expert annotation remains the reference standard but does not scale to large video collections or routine coaching workflows.
Markerless pose estimation offers a practical alternative to instrumented \acs{MOCAP}, yet public benchmarks for temporal phase segmentation in weightlifting remain scarce, and published pipelines are often difficult to reproduce exactly.

This manuscript introduces \emph{SnatchPhaseBench}, an evolving research artifact that couples a curated snatch dataset, a documented preprocessing pipeline, and a reproducibility-oriented evaluation framework.
At the time of writing, we have verified dataset reconstruction (\numwindows{} sliding windows from \numvideos{} videos of \numathletes{} athletes), athlete-level data splits, and a frozen \acs{LSTM} baseline protocol derived from prior thesis work.
Quantitative performance claims in saved source artifacts have \emph{not} yet been re-validated on the original trained checkpoint; benchmark comparisons against alternative temporal models are planned but not reported here.

The intended contribution is therefore methodological and infrastructural: a reproducible benchmark protocol for temporal phase segmentation rather than a single architecture.
Future revisions of this living manuscript will incorporate verified benchmark results, segment-level metrics, and public release details as those experiments are completed.
\end{abstract}

\noindent\textbf{Keywords:} temporal action segmentation; Olympic weightlifting; markerless pose estimation; reproducibility; sports biomechanics; benchmark

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_dataset}
\input{sections/04_methods}
\input{sections/05_experimental_protocol}
\input{sections/06_results}
\input{sections/07_discussion}
\input{sections/08_limitations}
\input{sections/09_conclusion}

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}
